Initial Analysis

### 2020-02-07 Initial_Analysis.Rmd
Exploring Colette's comment

@@

length(unique(Tresholded_T_Data$eez_name))

@@

>>>>

# Read Results For Carmelia

# Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))

@@

length(unique(Tresholded_T_Data$taxon_key))

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  )

# Makes sense?
# nrow(Tresholded_T_Data) + nrow(Discrete) == nrow(Clean_Results_Trans) # TRUE

#Number of discrete species #170

n_discrete <- Clean_Results_Trans %>% 
  filter(! taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
  group_by() %>% 
  summarize(length(unique(taxon_key))) %>% 
  pull()

@@

### UN Data exploration

```{r}

  UN_Regions %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(n_countries = length(unique(fishing_entity))) %>% 
  arrange(n_countries)

World_sf %>% 
  as.data.frame() %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_EEZ = sum())
